Environment affects specialisation of plants and pollinators

### 2019-12-03 paper/manuscript.Rmd
Reorder paraphaph in the methods to improve clarity

Next, we calculate the probability density function of the species distribution in environmental space. 
To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance. 
We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
The normalised density at that particular location [which we calculate using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability. 
We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.

>>>>

Next, we calculated the probability density function of the species distribution in environmental space. 
To determine the environmental space, we used the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we used the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance. 
We then determined the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
We used a kernel method to estimate this density and normalised it such that it ranges between zero and one. 
We used the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002] (as it has been proposed earlier) because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
Specifically, to calculate the probability density function we used `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
We then determined the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
The normalised density at that particular location [which we calculated using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability. 
The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.
